V1298~Tau with TESS: Updated Ephemerides, Radii, and Period Constraints from a Second Transit of V1298~Tau~e

### 2021-11-07 src/ms.tex
word trimming time

\documentclass[twocolumn]{aastex631}

@@

\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$. Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment. \sname was originally observed 6 years ago during \textit{K2} Campaign 4. Now, \sname has been re-observed during the extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess). Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images. We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level. While the shallower transits observed by \tess\ could be due to high-altitude hazes in the extended atmospheres of these young planets, we suspect the difference is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname. We additionally catch a transit of \planete, which transited only once during the \textit{K2} observations, and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart. We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain. Additionally, we find the transit depth for \planete to be $3\sigma$ deeper than what was measured from \textit{K2}. \sname is the target of several ongoing and future observations, including with the James Webb Space Telescope. These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.

@@

The youth of \sname (also K2-309 and [WKS96] 4) was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements of pre-main sequence stars in Taurus-Auriga \citep{frink1997}. An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}. A kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr. However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}. Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data \citep{johnson21}. While the precise age of \sname remains uncertain, most estimates fall in the 10--40~Myr range and we adopt $t \approx$~20--30~Myr.

@@

Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}). The letter is laid out as follows. We describe the observations and light curve extraction in Section~\ref{sec:observations}. In Section~\ref{sec:analysis}, we present our transit and stellar variability modeling. We additionally present a novel method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large gap between them. We provide transit mid-point dates and times for \planete for ground-based follow-up in the United States. In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii. We conclude in Section~\ref{sec:conclusions}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel ``Planets b, c, \& e"), the sum of the transits is blotted in black.} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We took a two-step approach to modeling any background contamination. First, we defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution. Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.

@@

Our final GP model for stellar variability and planet transits are shown in Figure~\ref{fig:transits}. There is a $\sim 1\%$ flare at \tess\ BKJD $\approx$ 4659.18 that we do not fit. We present zoom-ins on the individual transits in the \tess\ light curve. Per each panel, we present the GP model-removed flux (de-trended flux) and the best-fit transit models for each observed transit.

@@

Determining the period of a planet from two transits with a significant time gap between surveys has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}. Orbital periods that resulted in a likelihood $> 10^4$ are then ruled out. In our new method, we are fitting for discrete periods at each step of the MCMC sampler, rather than post-processing from our posterior. We take the following approach:

@@

We ran 5 chains with 500 tuning steps and 5000 draws. Similarly to the transit fits, we discarded the tuning steps before our analysis. Our results are presented in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.

@@

Using this method, we find the most likely period of \planete to be 50.748~days. We computed a $\chi^2$-fit to a Gaussian distribution using \texttt{lmfit} \citep{lmfit} and find the period to be $50.74 \pm 5.88$~days. Even at the lower limit, it is unlikely a transit of \planete will occur in the next orbit of Sector 44. This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb. If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in nearly 4 planet resonant chain.

Independent ground-based monitoring of the system for several days beyond the end of Sector 44 (UT 06 Nov 2021) may be able to observe another transit of the outermost known planet in this system. Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several transit midpoint events observable in Mountain Time [UTC-7], Pacific Time [UTC-8], and Hawaiian Time [UTC-10], given the top 5 most-likely periods for \planete at the end of Table~\ref{tab:table}.

@@

%Because \sname is young, it is expected that \allplanets have extended atmospheres due to high levels of stellar irradiation \citep{OwenWu2017} and are slowly evolving as atmospheric mass is lost. 
A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}. Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm][]{Ricker2015}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!b]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{figures/folded_compare.pdf}
\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black). The residuals between the \tess\ data and each fit are shown underneath. A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference. The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper. We speculate the variation in transit depths could be due to starspot crossing events.} \label{fig:compare}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:dilution}). We localized a 1-day window around each transit and computed the a $\chi^2$ fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial. We find the transit depths to decrease falling off of the pixels centered on \sname. While fitting the \tess\ PSF with a 2D Gaussian function is a good approach, it is not the perfect model. It is possible that we are including dilution from these other nearby bright ($T_\textrm{mag}< 14$) targets. This is especially true for TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$. A more carefully constructed PSF to these \tess\ pixels would potentially yield a less diluted light curve.

A change in transit depth could additionally be due to starspots, either from nearby source or from the surface of \sname. In the context of starspots on \sname, both starspot/active region crossing events, where the planets directly transit over these inhomogeneities, or asymmetric starspots/active region distributions located off the transit chord could lead to differences in transit depths and shapes. In the case of starspot crossing events, we would expect to see added variability to the transit shape. Assuming we are not underestimating our error bars, this is readily seen in the transit of \planetb, both in the \tess\ and \textit{K2} data (Figure~\ref{fig:compare}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{static/dilution.pdf}
\caption{The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. \sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $T_\textrm{mag} < 14$ are marked with blue x's.} \label{fig:dilution}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radius of \planete}

Contrary to \planetknown, we measure a transit radius that is $\sim 3\sigma$ larger in the new \tess\ data than what was found in the original \textit{K2} data.

The difference in radii could be consistent with a large scale height, low mean-molecular weight atmosphere around \planete \citep{deMooij12}. It is also possible the atmosphere of \planete is dominated by species with stronger absorption features at longer wavelengths, such as CO, H$_2$O, and CH$_4$ \citep{carter09}. Such measurements could be possible using a variety of ground-based instruments \citep[e.g.][]{line21} and would provide insight into the planet formation process and location of the \planete. However, future characterization of this atmosphere requires an exact period in order to plan additional ground-based follow-up.

@@

\cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data. The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and may not have the temporal resolution needed to unambiguously demonstrate starspot crossings. Future \tess\ 20-second and 2-minute data may yield insight into if there is evidence of starspot crossing events. Our transit of \planete from the FFIs shows some structure, particularly with a slight increase in transit depth around $t \approx 4648.8$~BKJD. At the 10-minute cadence, it is hard to rule out noise as the source of this structure. However if there is such evidence of starspot crossings in the higher-cadence \tess\ observations, it would be interesting if any of the events dilutes the transit enough to result in a similar transit depth to that which was seen in \textit{K2}.

@@

The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}

@@

\begin{deluxetable*}{l r r r r}[!ht]

>>>>

\documentclass[linenumbers,modern,twocolumn]{aastex631}

@@

\sname is a young (20--30~Myr) solar analogue hosting four transiting exoplanets with sizes between $0.5 - 0.9 R_J$. Given the system's youth,  it provides a unique opportunity to understand the evolution of planetary radii at different separations in the same stellar environment. \sname was originally observed 6 years ago during \textit{K2} Campaign 4. Now, \sname has been re-observed during the extended mission of NASA's Transiting Exoplanet Survey Satellite (\tess). Here, we present new photometric observations of \sname from the 10-minute \tess\ Full-Frame Images. We use the \tess\ data to update the ephemerides for \allplanets as well as compare newly observed radii to those derived from the \textit{K2} light curve, finding shallower transits for \planetknown in the redder \tess\ bandpass at the $1-2\sigma$ level. We suspect the difference in radii is due to starspot-crossing events or contamination from nearby faint stars on the same pixels as \sname. We additionally catch a second transit of \planete and present a new method for deriving the marginalized posterior probability of a planet's period from two transits observed years apart. We find the highest probability period for \planete to be in a near 2:1 mean motion resonance with \planetb which, if confirmed, could make \allplanets a 4 planet resonant chain. \sname is the target of several ongoing and future observations. These updated ephemerides will be crucial for accurately recovering transit events and understanding any future Doppler tomographic or transmission spectroscopy signals.

@@

The youth of \sname was initially established on the basis of its strong X-ray emission \citep{Wichmann1996}, high photospheric lithium abundance \citep{Wichmann2000}, and proper motion measurements \citep{frink1997}. An additional recent blind search for co-moving stars using Gaia DR1 astrometry data found \sname was co-moving with 8 other stars \citep[Group 29 in][]{Oh2017}. A kinematic study of the Taurus star-forming region \citet{Luhman2018} used Gaia DR2 data to extended the membership of this group and derived an age of $\sim$~40~Myr. However, more recent analyses based on Gaia EDR3 astrometry suggests \sname may belong to either the D2 or D3 subgroups of Taurus, both of which have estimated ages $\lesssim$10~Myr \citep{gaidos21, Krolikowski2021}. Other studies focused specifically on the \sname system have estimated its age to be 23$\pm$4~Myr from comparison with empirical and theoretical isochrones \citep{David2019b}, or 28$\pm$4~Myr from isochrone fitting to the \citet{Luhman2018} Group 29 membership list given Gaia EDR3 data \citep{johnson21}. While the precise age of \sname remains uncertain, most estimates fall in the 10--40~Myr range and we adopt $t \approx$~20--30~Myr.

@@

Here we report on newly acquired \tess\ observations of \sname which help to refine the orbital ephemerides of the transiting planets and enable comparison of the planet sizes inferred from two different telescopes with different bandpasses (\tess\ and \textit{Kepler}). The letter is laid out as follows. We describe the observations and light curve extraction in Section~\ref{sec:observations}. In Section~\ref{sec:analysis}, we present our light curve modeling and method for computing the marginalized posterior probability of a transiting planet's period from two transits observed with a large time gap. In Section~\ref{sec:radii}, we discuss the differences in measured transit parameters between \textit{K2} and \tess\ data and speculate on the causes for different measured radii. We conclude in Section~\ref{sec:conclusions}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[hbtp]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{figures/transits.pdf}
\caption{\sname extracted light curve from the \texttt{tica}-processed full-frame images for all of Sector 43 and the first orbit of Sector 44, with transits of \allplanets highlighted by color. Each subplot contains the raw, normalized \tess\ flux (top) and the GP model removed flux (de-trended flux; bottom). Top row: extracted light curve with over plotted with our best-fit GP model for stellar variability (black). Bottom three rows: zoomed-in regions around the transits present in the \tess\ data. The GP best-fit model is over-plotted on the raw, normalized flux. The best-fit transit models are over-plotted on the de-trended flux. For overlapping transits (sub-panel ``Planets b, c, \& e''), the sum of the transits is blotted in black.} \label{fig:transits}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We modeled the background within out GP. We defined a quadratic trend with respect to time for varying the background flux, where each polynomial coefficient was drawn from a normal distribution. Then, we generated a Vandermonde matrix ($A$) of time. This is a way of introducing a polynomial least-squares regression with respect to time. The final background flux was calculated by taking $bkg = A \cdot trend$.

@@

We present our final GP model for stellar variability, planet transits, and best-fit transit models in Figure~\ref{fig:transits}. There is a $\sim 1\%$ flare at \tess\ BKJD $\approx$ 4659.18 that we do not fit.

@@

Determining the period of a planet from two transits with a significant time gap between surveys has previously been constrained by fitting for orbital periods using MCMC sampling, phase-folding all available transits on the derived transit times and periods, and computing a reduced-$\chi^2$ fit to a flat line \citep{becker19}. Orbital periods that resulted in a likelihood $> 10^4$ are then ruled out. In our new method, we are fitting for discrete periods at each step of the MCMC sampler, rather than post-processing from our posterior.

@@

We ran 5 chains with 500 tuning steps and 5000 draws. We discarded the tuning steps before our analysis. Our results are presented in Figure~\ref{fig:period_e}, where we plot the median period for each tested harmonic against the posterior probability of each harmonic.

@@

We find the most likely period of \planete to be 50.748~days. We computed a $\chi^2$-fit to a Gaussian distribution using \texttt{lmfit} \citep{lmfit} and find the period to be $50.74 \pm 5.88$~days. Even at the lower limit, it is unlikely a transit of \planete will occur in the 2\textsuperscript{nd} orbit of Sector 44. This derived period estimate suggests that \planete is in a near 2:1 mean motion resonance with \planetb. If the period of \planete is confirmed to be within the presented range, this could indicate that \allplanets are in nearly 4 planet resonant chain.

Independent ground-based monitoring of the system may be able to observe another transit of the outermost known planet in this system. Using the Transit Service Query Form on the NASA Exoplanet Archive \citep{Akeson2013}, we provide several potential transit midpoint events, given the top 5 most-likely periods for \planete, at the end of Table~\ref{tab:table}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!htb]
\begin{center}
\includegraphics[width=\textwidth,trim={0.25cm 0 0 0}]{static/combined_together.pdf}
\caption{Left: Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black). The residuals between the \tess\ data and each fit are shown underneath. Top right: A comparison of measured $R_p/R_\star$ are presented with a 1-to-1 line plotted in black for reference. The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper. Bottom right: The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. We speculate the variation in transit depths could be due to contamination from nearby bright stars or starspot crossing events.} \label{fig:compare}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

A shallower transit depth at redder wavelengths is supported by the dusty outflow model presented in \citep{wang19}, while transits in the optical probe lower atmospheric pressures, resulting in larger transit depths \citep{gao20}. Therefore, the difference in transit depths could be due to the difference in bandpass wavelength coverage between \textit{Kepler} \citep[400-900~nm;][]{Howell2014} and \tess\ \citep[600-1000~nm][]{Ricker2015}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{figure}[!b]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{figures/folded_compare.pdf}
\caption{Phase-folded \tess\ data (gray) with the new best-fit model (color) compared to the original \textit{K2} data (black). The residuals between the \tess\ data and each fit are shown underneath. A comparison of measured $R_p/R_\star$ are presented at the bottom, with a 1-to-1 line plotted in black for reference. The transit depths for \planetknown are shallower in the new \tess\ data, while the transit depth for \planete is deeper. We speculate the variation in transit depths could be due to starspot crossing events.} \label{fig:compare}
\end{center}
\end{figure}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We check for signs of dilution by creating light curves for individual pixels around \sname and measure the transit depths of \planetb and \planete (Figure~\ref{fig:compare}). We localized a 1-day window around each transit and computed the a $\chi^2$ fit using a transit model computed with \texttt{batman} \citep{Kreidberg15} and an underlying 2\textsuperscript{nd} order polynomial. We find the transit depths to decrease falling off of the pixels centered on \sname. While fitting the \tess\ PSF with a 2D Gaussian function is a reasonable approximation, it is not the perfect model. It is possible that this light curve is diluted from nearby stars, including TIC~15756226, which is the closest (separation $= 49.15\arcsec$) star with $T_\textrm{mag} = 13.09$.

A change in transit depth could additionally be due to starspots, either from a nearby source or from the surface of \sname. In the context of starspots on \sname, both starspot/active region crossing events, where the planets directly transit over these inhomogeneities, or asymmetric starspots/active region distributions located off the transit chord could lead to differences in transit depths and shapes. In the case of starspot crossing events, we would expect to see added variability to the transit shape. Assuming we are not underestimating our error bars, this is readily seen in the transit of \planetb, both in the \tess\ and \textit{K2} data (Figure~\ref{fig:compare}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{figure}[!t]
\begin{center}
\includegraphics[width=0.465\textwidth,trim={0.25cm 0 0 0}]{static/dilution.pdf}
\caption{The change in $R_p/R_\star$ as a function of pixel for \planetb (top) and \planete (bottom) overlaid with a sky image of \sname taken with the Digitized Sky Survey (DSS) r-band. \sname is highlighted by the white circle; nearby sources with \tess\ magnitudes $T_\textrm{mag} < 14$ are marked with blue x's.} \label{fig:dilution}
\end{center}
\end{figure}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Radius of \planete}

Contrary to \planetknown, we measure a transit radius that is $\sim 3\sigma$ larger in the new \tess\ data than what was found in the original \textit{K2} data \citep{David2019a}. The difference in radii could be consistent with a large scale height, low mean-molecular weight atmosphere around \planete \citep{deMooij12}. It is also possible the atmosphere of \planete is dominated by species with stronger absorption features at longer wavelengths, such as CO, H$_2$O, and CH$_4$ \citep{carter09}. %Such measurements could be possible using a variety of ground-based instruments \citep[e.g.][]{line21} and would provide insight into the planet formation process and location of the \planete. However, future characterization of this atmosphere requires an exact period in order to plan additional ground-based follow-up.

@@

%\cite{morris17} demonstrated the ability to detect starspot crossing events in short-cadence \textit{Kepler} data. The original \textit{K2} observations for \sname are at the long-cadence observing mode ($\sim 30$-minutes) and may not have the temporal resolution needed to unambiguously demonstrate starspot crossings. 
Future \tess\ 20-second and 2-minute data may have the temporal resolution needed to yield insight into if there is evidence of starspot crossing events. Our transit of \planete from the FFIs shows some structure. At the 10-minute cadence, it is hard to rule out noise as the source of this structure. However if there is such evidence of starspot crossings in the higher-cadence \tess\ observations, it would be interesting if any of the events dilutes the transit enough to result in a similar transit depth to that which was seen in \textit{K2}.

@@

%The Python code used to access the data, process and model the light curve, and reproduce the tables and figures are made publicly available.\footnote{\url{https://github.com/afeinstein20/v1298tau_tess}}

@@

\begin{deluxetable*}{l r r r r}[hbtp]
